Exploring probability distributions for bivariate temporal granularities

### 2019-11-24 main.Rmd
example for AH included

**Discussion**: Example showing aperiodic granularities relating two linear granularities each with bottom granularities are visually depicted in a series of slots in \autoref{fig:aperiodic-gran}. Each granule is represented by a box. Similar to \autoref{fig:circular-gran}, the granules that overlap share elements from the underlying time domain and the first slot shows the index set and the bottom granularity. 
Two linear granularities AG and AH are considered, where $AG = Alter^{5}_{(1,-1)}(BG, Group_3(BG))$ and $AH = Alter^{12}_{(1,-2)}(BG, Group_7(BG))$. This implies that AG is made up of shrinking every 1st granule of Group_3(BG) by 1 and AH is made up of shrinking every 1st granule of Group_3(BG) by 2. Number of granules of AG and AH in each period of BG is 2, but the number of granules of BG in each of those granules are different. A(BG, AG) and A(BG, AH) are repetitive categorisation of time, similar to circular granularities, except that the number of granules of BG is not necessarily the same across different granules of AG or AH. For AG, R' = 2, P'= 5, $T_0$ = {0,1} and $T_1$ = {2, 3, 4}, suppose we want to compute A(BG,AG)(8), then since $8 \in T_{3}$

\begin{equation} \label{eq4}
\begin{split}
A(BG,AG)(8) & = BG(8 - \sum_{w=0}^{3-1}\vert T_{w \mod 2}\vert) \\
  & = BG(8 - \sum_{w=0}^{2}\vert T_{w\mod 2}\vert) \\
  & = BG(8 - \sum_{w=0}^{2}\vert T_{w\mod 2}\vert) \\
  & = BG(8 - \vert T_{0 \mod 2}\vert - \vert T_{1 \mod 2}\vert - \vert T_{2 \mod 2}\vert) \\
  & = BG(8 - 2*\vert T_{0 \mod 2}\vert - \vert T_{1 \mod 2}\vert) \\
  & = BG(8 - 2.2 - 3) \\
  & = BG(1) \\
\end{split}
\end{equation}

```{r aperiodic-gran, echo=FALSE,out.width = "100%",fig.cap="\\label{fig:circular-gran} Relating circular granularities and bottom linear granularity "}
knitr::include_graphics("Figs/aperiodic-gran.png")
```

@@

The linear granularities G, H, G1 and G2 considered in the definitions of both circular and aperiodic granularities are periodic with respect to the bottom granularity. The only difference is G, H have regular mapping, whereas, G1 and G2 have irregular mapping with respect to BG.

>>>>

**Discussion**: Example showing aperiodic granularities relating two linear granularities each with bottom granularities are visually depicted in a series of slots in \autoref{fig:aperiodic-gran}. Each granule is represented by a box. Similar to \autoref{fig:circular-gran}, the granules that overlap share elements from the underlying time domain and the first slot shows the index set and the bottom granularity. 
Two linear granularities AG and AH are considered, where $AG = Alter^{5}_{(1,-1)}(BG, Group_3(BG))$ and $AH = Alter^{12}_{(1,-2)}(BG, Group_7(BG))$. This implies that AG is made up of shrinking every 1st granule of Group_3(BG) by 1 and AH is made up of shrinking every 1st granule of Group_3(BG) by 2. Number of granules of AG and AH in each period of BG is 2, but the number of granules of BG in each of those granules are different. A(BG, AG) and A(BG, AH) are repetitive categorisation of time, similar to circular granularities, except that the number of granules of BG is not necessarily the same across different granules of AG or AH. For AG, R' = 2, P'= 5, $T_0$ = {0,1} and $T_1$ = {2, 3, 4}. For AH, R' = 2, P'= 12, $T_0$ = {0, 1, 2, 3, 4, 5, 6} and $T_1$ = {7, 8, 9, 10, 11}, then we will have \ref{eq:eq4} and  \ref{eq:eq5}.

\begin{equation} \label{eq4}
\begin{split}
A(BG,AG)(8) & = BG(8 - \sum_{w=0}^{3-1}\vert T_{w \mod 2}\vert) , since 8 \in T_{3} \\
  & = BG(8 - \sum_{w=0}^{2}\vert T_{w\mod 2}\vert) \\
  & = BG(8 - \sum_{w=0}^{2}\vert T_{w\mod 2}\vert) \\
  & = BG(8 - \vert T_{0 \mod 2}\vert - \vert T_{1 \mod 2}\vert - \vert T_{2 \mod 2}\vert) \\
  & = BG(8 - 2*\vert T_{0 \mod 2}\vert - \vert T_{1 \mod 2}\vert) \\
  & = BG(8 - 2.2 - 3) \\
  & = BG(1) \\
\end{split}
\end{equation}

\begin{equation} \label{eq5}
\begin{split}
A(BG,AH)(10) & = BG(10 - \sum_{w=0}^{1-1}\vert T_{w \mod 2}\vert) \\ , 10 \in T_{1}
  & = BG(10 - \sum_{w=0}^{0}\vert T_{w\mod 2}\vert) \\
  & = BG(10 - \vert T_{0 \mod 2}\vert) \\
  & = BG(10 - \vert T_{0}\vert) \\
  & = BG(10 - 7) \\
  & = BG(3) \\
\end{split}
\end{equation}

```{r aperiodic-gran, echo=FALSE,out.width = "100%",fig.cap="\\label{fig:circular-gran} Relating circular granularities and bottom linear granularity "}
knitr::include_graphics("Figs/aperiodic-granv1.png")
```

@@

The linear granularities G, H, AG and AH considered in the definitions of circular and aperiodic granularities are all periodic with respect to the bottom granularity. The only difference is G, H have regular mapping, whereas, G1 and G2 have irregular mapping with respect to BG.
